Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-14 3dpas_intro.tex
Abstract refinement.

\begin{abstract}

  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed. Often the
  datasets, their locations, availability, analysis and associated scheduling
  decisions are time-dependent. Collectively these give rise to dynamic
  distributed data intensive applications.  The characteristics, requirements,
  and software systems for the analysis of large volumes of ``static'' data have
  received significant attention; dynamic, distributed and data intensive have
  received relatively less. This work will ameliorate the state by surveying
  several representative application scenarios, to provide a common conceptual
  framework to understand them as well as examining the infrastructure used in
  support of applications.

%   Applications need access
%   to these disparate data-sets and to the methods that operate on
%   them.  Data-intensive applications need first-class support for
%   distributed heterogeneous platform execution.

% The 3DPAS Research Theme (funded by the eSI, Edinburgh and US NSF)
% investigated applications that have these characteristics; in other
% words, it operated at the triple point of  {\it distributed} and {\it dynamic} and
% {\it data-intensive} (D3) attributes.  This document represents the conclusions
% of the 3DPAS Theme.

>>>>

\begin{abstract}
  A common feature across many science and engineering applications is the
  amount and diversity of data and computation that must be integrated to yield
  insights. Often data is increasingly large-scale and distributed; their
  location, availability and properties are time-dependent. Collectively these
  give rise to dynamic distributed data intensive applications. ``Static'' data
  have received significant attention.  The characteristics, requirements, and
  software systems for the analysis of large volumes of dynamic, distributed and
  data intensive have however received relatively less. This paper surveys
  several representative dynamic distributed data-intensive application
  scenarios, provides a common conceptual framework to understand them as well
  as examines the infrastructure used in support of applications.
